\begin{thebibliography}{7}

\bibitem{tabrizi}
{S. S. Tabrizi and N. Cavus, “A Hybrid KNN-SVM Model for Iranian License Plate Recognition,” \emph{Procedia Computer Science}, vol. 102, pp. 588–594, 2016.}

\bibitem{gou2014}
{C. Gou, K. Wang, Z. Yu, and H. Xie, “License plate recognition using MSER and HOG based on ELM,” \emph{Proceedings of 2014 IEEE International Conference on Service Operations and Logistics, and Informatics}, 2014.}

\bibitem{gou2016}
{C. Gou, K. Wang, Y. Yao, and Z. Li, “Vehicle License Plate Recognition Based on Extremal Regions and Restricted Boltzmann Machines,” \emph{IEEE Transactions on Intelligent Transportation Systems}, vol. 17, no. 4, pp. 1096–1107, 2016.}

\bibitem{rasheed}
{S. Rasheed, A. Naeem, and O. Ishaq, “Automated Number Plate Recognition Using Hough Lines and Template Matching,” \emph{Proceedings of the World Congress on Engineering and Computer Science}, vol. 1, pp. 24–26, 2012.}

\bibitem{gonzalez}
{R. C. Gonzalez and R. E. Woods, \emph{Digital Image Processing}, 4th ed. Pearson, 2017.}

\bibitem{ragb}
{H. K. Ragb and V. K. Asari, “Multi-feature fusion and PCA based approach for efficient human detection,” \emph{2016 IEEE Applied Imagery Pattern Recognition Workshop (AIPR)}, 2016.}

\bibitem{shih}
{F. Y. Shih, \emph{Image Processing and Pattern Recognition: Fundamentals and Techniques}, 1st ed. Wiley-IEEE Press, 2010.}

\bibitem{comvis}
{"Computer Vision CITS4240: Lab 6", [Online]. Available: http://teaching.csse.uwa.edu.au/units/CITS4240/Labs/Lab6/lab6.html [Accessed: 16-Apr-2019].}

\bibitem{rectangle}
{"Diagonals of a Rectangle", [Online]. Available: https://www.mathopenref.com/rectanglediagonals.html [Accessed: 13-May-2019].}

\bibitem{oechsle}
{O. Oechsle, "Finding Straight Lines with the Hough Transform", 2012. [Online]. Available: http://vase.essex.ac.uk/software/HoughTransform/ [Accessed: 16-Apr-2019].}

\bibitem{hog}
{N. Dalal and B. Triggs, “Histograms of Oriented Gradients for Human Detection,” \emph{Proceedings of the 2005 IEEE Computer Society Conference on Computer Vision and Pattern Recognition (CVPR’05)}, Jul. 2005.}

\bibitem{svm}
{Y. Ma and G. Guo, \emph{Support Vector Machines Applications}, 2014th ed. New York: Springer, 2014.}

\bibitem{markham}
{K. Markham, "Simple Guide to Confusion Matrix Terminology", 2014. [Online]. Available: https://www.dataschool.io/simple-guide-to-confusion-matrix-terminology/ [Accessed: 22-Apr-2019].}

\bibitem{nugroho}
{A. Nugroho and K.R.R. Wardhani, "Aplikasi Sistem Pembaca Plat Nomor Mobil Menggunakan Pengolahan Citra dan Metode Learning Vector Quantization," \emph{Institut Teknologi Harapan Bangsa (ITHB)}, 2011.}

\bibitem{polri}
{"Peraturan Kapolri Nomor 5 tahun 2012 tentang Registrasi dan Identifikasi Kendaraan Bermotor", [Online]. Available: http://kepri.polri.go.id/pid/wp-content/uploads/2019/01/PERATURAN-KAPOLRI-NOMOR-5-TAHUN-2012-TENTANG-REGISTRASI-DAN-IDENTIFIKASI-KENDARAAN-BERMOTOR.pdf [Accessed: 22-Apr-2019]}

\bibitem{ashtari}
{A. H. Ashtari, M. J. Nordin, and M. Fathy, “An Iranian License Plate Recognition System Based on Color Features,” \emph{IEEE Transactions on Intelligent Transportation Systems}, vol. 15, no. 4, pp. 1690–1705, 2014.}

\bibitem{gryimage}
{R. Fisher, et all, "Grayscale Images", 2003. [Online]. Available: https://homepages.inf.ed.ac.uk/rbf/HIPR2/gryimage.htm [Accessed: 26-Jun-2019]}

%\bibitem{10}
%{R. C. Gonzalez and R. E. Woods, \emph{Digital Image Processing}, $2^{nd}$ ed. Prentice Hall, 1992.}
%\bibitem{12}
%{“CS231n Convolutional Neural Networks for Visual Recognition”, \emph{CS231n}. [Online]. Available: cs231n.github.io/convolutional-networks/. [Accessed: 19-Nov-2017].}
%\bibitem{13}
%{S. Haykin, \emph{Neural Networks and Learning Machines}, $3^{rd}$ ed. Pearson, 2008.}
%\bibitem{14}
%{T. Babb, "How a Kalman filter works, in pictures", \emph{Bzarg}, 2015. [Online]. Available: http://www.bzarg.com/p/how-a-kalman-filter-works-in-pictures/. [Accessed: 11- Dec- 2017].}
%\bibitem{15}
%{G. Zhang, L. Tian, et al., “Robust real-time human perception with depth camera”, \emph{in ECAI 2016: 22nd European Conference on Artificial Intelligence}, 29 August-2 September 2016. IOS Press, 2016, vol. 285, p. 304.}
%\bibitem{16}
%{H. Habibi Aghdam and E. Jahani Heravi, \emph{Guide to Convolutional Neural Networks}, 2017.}
%\bibitem{17}
%{S. Khan, H. Rahmani, S. A. A. Shah, and M. Bennamoun, \emph{A Guide to Convolutional Neural Networks for Computer Vision}, vol. 8, no. 1. 2018.}
%\bibitem{18}
%{Stephanie, “Jaccard Index / Similarity Coefficient'', \emph{Statistics How To}, 2016. [Online]. Available: http://www.statisticshowto.com/jaccard-index/. [Accessed: 20-May-2018].}
%\bibitem{19}
%{J. Jordan, “Setting the learning rate of your neural network”, \emph{Jeremy Jordan}, 2018. [Online]. Available:https://www.jeremyjordan.me/nn-learning-rate/. [Accessed: 22-May-2018].}
%\bibitem{20}
%{A. Sachan, “Zero to Hero: Guide to Object Detection using Deep Learning: Faster R-CNN, YOLO, SSD”, \emph{Learn Machine Learning, AI \& Computer Vision}, 2017. [Online]. Available:http://cv-tricks.com/object-detection/faster-r-cnn-yolo-ssd/. [Accessed: 5-June-2018].}
%\bibitem{21}
%{M. Tyka, “Inceptionism: Going Deeper into Neural Networks”, \emph{Google AI Blog}, 2015. [Online]. Available:https://ai.googleblog.com/2015/06/inceptionism-going-deeper-into-neural.html. [Accessed: 13-June-2018].}

\end{thebibliography}